The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-12-04 article.tex
Add effect of taxa

@@

>>>>

\item To see the effect of the number of taxa on the relation 
between $s$ and $e$, we simulate phylogenies
for different number of extant taxa $n$. We use values of $n$
of 50, 100 and 200 extant taxa, as this will result in phylogenies
that are big enough to be useful, yet small of enough to
be computationally feasible. For the different values of $n$, we show
the relation between $s$ and $e$ in figure \ref{fig:5} and its effect
on the variance of $e$ in figure \ref{fig:6}.

$s$ spread equally from zero (no multiple-birth
event, thus a BD model) to one (species are created only from multiple-birth
events) and three intermediate values of 0.25, 0.5 and 0.75. Aggregating all
components of $s$, we show the effect of $s$ on $e$ in figure \ref{fig:1}.

@@

\item We expected the effect of the number of taxa on the relation
between $s$ and $e$ to be neutral (figure \ref{fig:h_5}). 
Figure \ref{fig:5} shows the effect 
measured in this experiment.

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_5.png}
  \caption{
    The effect of number of taxa on the relation between s on e
  }
  \label{fig:5}
\end{figure}

\item We expected the effect of the number of taxa on the variance
of $e$ for similar values of $s$ to decrease (figure \ref{fig:h_6}). 
Figure \ref{fig:6} shows the effect 
measured in this experiment.

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_6.png}
  \caption{
    The effect of number of taxa on the variance in e
    for similar values of s
  }
  \label{fig:6}
\end{figure}
